\section*{VICTORY POINTS}
Each downed aircraft gives victory
points as follows:
B-52: 10 VP
F-111 or ECM: 2 VP
F-4 or NV fighter: 1 VP
Other VPs as of Bombing Tables,
and:
Destroyed airfield: 5 VP
US PM hits ‘0’: 20 VP to NV player
First bombing of Hanoi/Haiphong:
10/5 VP to NV player

\section*{SCENARIOS}
1. Campaign scenario
Date: 17/12 - 28/12
US Forces:
132 B-52
30 F-111
182 F-4
NV Forces:
40 fighters
1000 SAMs
Airfields intact
US player is first player, US PM: 6
Reinforcements: US, 24/12 7 ECM
aircraft
Victory conditions:
[Victory Point Totals]
US:
0-10 Draw
11-20 Business as usual
21-30 Tactical victory—Fly the
friendly skies of Nam
31+ War won militarily to be lost
by politicians
NV:
0-10 Draw (victory, really!)
20-11 Tactical victory
21-30 Strategic victory: Go south and
win the war

2. First Phase Scenario
Date: 17/12 - 24/12
Forces: as campaign
Victory conditions: as campaign
Special rule: 20 VP to US player if
SAM supply falls below 300
3. Second Phase Scenario
Date: 25/12 - 28/12
US Forces:
123 B-52
28 F-111
120 F-4
6 ECM aircraft
NV Forces:
32 fighters
400 SAMs
Airfields 2 and 6 destroyed
Victory points: 30 to VN player,
US PM: 4
Victory conditions: as campaign game

TAU CETI 2015AD
“We designed TAU CETI because we were fed up
with all the hypercomplex Science Fiction games
out today. With the present ‘state of the art’
surely it must be possible to design a game
simple in play yet with a complex game system?
We think we have succeeded.”
Tau Ceti is a challenging SF game simulating tactical ground
combat on an alien planet in the year 2015. The two different
races, Kra (red lizard-type and vicious, but with two legs) and
H’ren (blue-furred mouse-like creatures but with two arms
and two legs) fight for control of the planet and employ two
different tactics: Kra employing strong Plasma Launchers
and Heavy Assault Vehicles—and H’ren using hordes of Light
Assault Vehicles and Hovercarriers.
Three terrain levels and three altitude levels enable the play-
ers to fight a semi-three dimensional battle and without paper-
work—a simple marker tells you on which altitude a unit is on.
Hovering, transportation, two different combat doctrines (P
and I Combat), line of sight, spotting, remotes (ground/aerial
bombs/mines) all play important roles to make this game a fun
and fast-playing “simulation”. And don’t forget the ten
scenarios. These will keep you playing till the first astronaut
steps on Mars!
A high level of physical quality is maintained. The three-color
map is printed in tints of black, green, and brown. The 130
back-printed die-cut counters are three-colored and bear
silhouettes of the combat units. The rulebook is illustrated and
typeset. Last but not least, the front cover bears a wonderful
illustration by the artists. Eddie Eddings and Jim Newsome
(and a drawing of Jim’s appears inside the game). Our game
is packaged in a ziplock bag for easy storage and to keep the
price low. In fact, ridiculously low.
The game is available through larger stores around the world,
or directly from us:

SWEDISH GAME PRODUCTION
Box 18
S-590 40 Kisa, Sweden

